---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



# The `bggscraper` library

<!-- badges: start -->
<!-- badges: end -->

`bggscraper` is an R package that scrapes all sorts of (publicly accessible) data from the [Board Game Geek](boardgamegeek.com) website. It depends heavily on the [BGG XML API2](https://boardgamegeek.com/wiki/page/BGG_XML_API2) library.

***Note that this is a work in progress. However, I intend to make it useful and usable soon (by end of March, 2023).***

Using this library, you may scrape the following info (among others):

* list of [top 5000 board games](https://boardgamegeek.com/search/boardgame?advsearch=1&q=&sort=rank) as per the rankings on BGG.
* details on board games and board game expansions (i.e., categories, mechanics, designers, etc.)
* BGG users' games collections, including what they own as well as what they hope to play or buy in the future.
* Info on users themselves.
* list of games are hot nowadays.
* Information on plays of a certain game for one or more users.
* geeklists, forum lists, forums, threads, guilds pertaining to a certain board game id.


## Installation

You can install the development version of bggscraper from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alizat/bggscraper")
```

## Examples

This is an example that shows how to retrieve information on a particular user's (board game) collection:

```{r, echo=TRUE}
library(bggscraper)

# get a user's game collection
user <- 'alizat'
collection_items <- user_collection(user)

# get details for each item in user's collection
games_details <- list()
for (i in 1:nrow(collection_items)) {
    # get details for current item
    games_details[[as.character(collection_items$object_id[[i]])]] <- game_info(collection_items$object_id[[i]])
    
    # sleep 5 seconds (to avoid getting blocked for too many requests in short time)
    Sys.sleep(5)
}

# print info for the first game
print(games_details[[1]], n = 100)
```

This is an example that shows to retrieve the current top 10 board games ids as per [BGG's rankings](a)

```{r, echo=TRUE}
library(bggscraper)

# top 10 ranked games on BGG
top_K_games_ids <- top_k_games_ids(k = 10)

# get details for each item in user's collection
games_details <- list()
for (id in top_K_games_ids) {
    # get details for current game
    games_details[[id]] <- game_info(id)
    current_games_details <- games_details[[id]]
    
    # print current game id and name
    print(paste0(id, ': ', current_games_details$value[current_games_details$feature == 'name']))
    
    # sleep 5 seconds (to avoid getting blocked for too many requests in short time)
    Sys.sleep(5)
}
```

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>. -->

<!-- You can also embed plots, for example: -->

<!-- ```{r pressure, echo = FALSE} -->
<!-- plot(pressure) -->
<!-- ``` -->

<!-- In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN. -->
